### 2015-11-24 p01-ch01-2012/paper.tex
Add publication information to chapter abstracts

\chapter[Application-Level Scheduling]{Programming and Deployment of Active Objects with Application-Level Scheduling%
\footnote{This work is partially supported by the EU FP7-231620 project: HATS.}
}
% 
\label{ch:p01:ch01}
% 
\chapterauthor{Behrooz Nobakht, Frank S. de Boer, Mohammad Mahdi Jaghoori,  Rudolph Schlatte}

% --- Author Metadata here ---
% \conferenceinfo{SAC'12}{March 25-29, 2012, Riva del Garda, Italy.}
% \CopyrightYear{2011}
% \crdata{978-1-4503-0857-1/12/03}
% --- End of Author Metadata ---

% \title{Programming and Deployment of Active Objects with Application-Level Scheduling%
% \titlenote{This work is partially supported by the EU FP7-231620 project: HATS.}
% }

% \numberofauthors{2}  %set to two to enable longer lines for names and

% \author{
% \alignauthor Behrooz Nobakht\\
% 	\affaddr{Leiden Institute of Advanced Computing}\\
% 	\affaddr{Universiteit Leiden, Leiden, The Netherlands}\\
% 	\email{bnobakht@liacs.nl}
% \alignauthor Frank S. de Boer\\
% 	\affaddr{Centrum Wiskunde and Informatica}\\
% 	\affaddr{Amsterdam, The Netherlands}\\
% 	\email{frb@cwi.nl}
% \and
% \alignauthor Mohammad Mahdi Jaghoori\\
% 	\affaddr{Centrum Wiskunde and Informatica}\\
% 	\affaddr{Amsterdam, The Netherlands}\\
% 	\email{jaghoori@cwi.nl}
% \alignauthor Rudolf Schlatte\\
% 	\affaddr{University of Oslo}\\
% 	\affaddr{Oslo, Norway}\\
% 	\email{rudi@ifi.uio.no}
% }

@@

@@

>>>>

\chapter[Application-Level Scheduling]{Programming and Deployment of Active Objects with Application-Level Scheduling%
\footnote{This work is partially supported by the EU FP7-231620 project: HATS.}}
% 
\label{ch:p01:ch01}
% 
\chapterauthor{Behrooz Nobakht, Frank S. de Boer, Mohammad Mahdi Jaghoori,  Rudolph Schlatte}

@@

\subparagraph*{Conference Publication}
\emph{Proceedings of the 27th Annual ACM Symposium on Applied Computing -- ACM SAC 2012, Pages 1883--1888, DOI \smalltt{10.1145/2245276.2232086}}

@@

\lstset{escapeinside={}{}}
